---
title: "Assignment2"
author: "Haojin Li (Declan)"
date: "2020/7/23"
output:
  pdf_document:
    toc: yes
  html_document:
    toc: yes
    df_print: paged
---


# 3.2.4 Exercises
---

## 1. Run `ggplot(data = mpg)`. What do you see?

```{r}
library(ggplot2)
ggplot(data = mpg)

```
I see nothing...

## 2. How many rows are in `mpg`? How many columns?
```{r}
dim(mpg)
```

## 3. What does the `drv` variable describe? Read the help for `?mpg` to find out.

```{r}
?mpg()


# `drv` is the type of drive train, where `f = front-wheel drive`, `r = rear wheel drive`, `4 = 4wd`
```


## 4. Make a scatterplot of `hwy` vs `cyl`.

```{r}
library(ggplot2)
ggplot(mpg, aes(hwy, cyl)) + geom_point()
# plot(mpg$hwy, mpg$cyl, xlab="hwy", ylab="cyl")

```

### 5. What happens if you make a scatterplot of `class` vs `drv`? Why is the plot not useful?
```{r}
library(ggplot2)
ggplot(mpg, aes(class, drv)) + geom_point()
```

There's no correlation between `class` and `drv`.


# 3.3.1 Exercises
---

## 1
```{r}
ggplot(data = mpg) + 
  geom_point(mapping = aes(x = displ, y = hwy), color = "blue")
```


## 2

```{r}
mpg
```


### Catagorical Variables
manufacturer
model
trans
drv
fl
class

### Continuous Variables
displ
year
cyl
cty
hwy

## 3

```{r}
ggplot(mpg, aes(x = displ, y = hwy, colour = cty)) +
  geom_point()
```


```{r}
ggplot(mpg, aes(x = displ, y = hwy, size = cty)) +
  geom_point()
```


```{r eval=FALSE, include=FALSE}
ggplot(mpg, aes(x = displ, y = hwy, shape = cty)) +
  geom_point()

# A continuous variable can not be mapped to shape
```

